Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-11-09 paper/paper.tex
Tweaks

The performance of both the biased heuristics and the degree heuristic are very similar: the
degree-biased heuristic has slightly worse performance below a 100s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using dots and crosses respectively. On the
$x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure random + restarts.
Points on the outer axes represent instances which timed out with one heuristic but not the other.
This plot shows that on a case by case basis, randomness can make a large difference to individual
satisfiable instances.

@@

?? maybe some engineering aspects: look at what happens without nogoods in
\cref{figure:scatter-nogoods}, and at performance with restarts on degree in
\cref{figure:scatter-overheads}.

@@

A bit of text here.

@@

>>>>

The performance of both of the biased heuristics and the degree heuristic are very similar: the
degree-biased heuristic has slightly worse performance below a 100s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using coloured shapes and black dots respectively.
On the $x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure the degree-biased
heuristic. Points on the outer axes represent instances which timed out with one heuristic but not
the other.  This plot shows that despite the aggregate performance being very similar, on an case by
case basis, the two heuristics can make a large difference to the performance of satisfiable
instances.

@@

@@

?? engineering aspects: look at what happens without nogoods in \cref{figure:scatter-nogoods}, and
at performance with restarts on degree in \cref{figure:scatter-overheads}.

@@

?? effects of restart policies, \cref{figure:restart-policies}.
